\vspace{-2cm} Government websites as data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2018-09-28 paper/manuscript.tex
addressed a point about a sentence that looked like it might imply that there are scenarios where our method doesn't work by simply removing the sentence (see comment in revision memo for an explanation)

We then take several steps to pre-process the data as required for subsequent the subsequent analysis. Pre-processing choices should be contingent on the analysis being conducted with the text later and can have significant effects on the outcomes of an analysis \citep{denny2018text}. The steps taken here should therefore not be seen as universally applicable to all analyses of government website data.

>>>>

We then take several steps to pre-process the data as required for the subsequent analysis. Pre-processing choices should be contingent on the analysis being conducted with the text later and can have significant effects on the outcomes of an analysis \citep{denny2018text}. %With the exception of file type conversion and boilerplate removal, the pre-processing steps taken here should therefore not be seen as universally applicable to all analyses of government website data.
